Symbolic Weighted Language Models and\\ Parsing over Infinite Alphabets

### 2021-06-09 main.tex
format LIPIcs

% default style article.cls
\input{main-article}

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

@@

%% algorithms
%\usepackage{algorithm} 
%\usepackage{program}

@@

\noindent
Iterate the following for all $p_1\in P$ and $q_1, q_2 \in Q$:
for all $p_2\in P$ and $q_3 \in Q$,
\[
\wei'_1\bigl( \< p_1, q_1>, \< p_2, q_3>\bigr) \opluseq 
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2) 
\otimes 
\wei'_1\bigl( \< p_1, q_2>, \< p_2, q_3>\bigr)
\]
and
\[
\final'(p_1, q_1) \opluseq 
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2) 
\otimes \final'(p_1, q_2)
\] 
\marginpar{\tiny proof correctness}
\qed
\end{proof}

@@

\begin{algo}[best search for \SWVPA]\label{algo:Dijkstra}
\textbf{initially} 
let $\Q = (Q \times Q) \cup (Q \times P \times Q)$, %contains all 
and let 
$d_\bot(q_1, q_2) = d_\top(q_1, p, q_2) = \one$ if $q_1 = q_2$ and
$d_\bot(q_1, q_2) = d_\top(q_1, p, q_2) = \zero$ otherwise.

\smallskip\noindent
\textbf{while} $\Q$ is not empty

\noindent\quad
\textbf{extract} $\< q_1, q_2>$ or $\< q_1, p, q_2>$ from $\Q$

\noindent\quad
such that $d_\bot(q_1, q_2)$, resp. $\bigoplus_{c\in \Omegac} d_\top(q_1, p, q_2)(c)$,
is minimal in $\Semiring$ wrt $\leq_\oplus$.

\noindent\quad 
%\textbf{for all} $q_0, q_3 \in Q$ 
\textbf{update} $d_\bot$ with $\< q_1, q_2>$ or $d_\top$ with $\< q_1, p, q_2>$
(Figure~\ref{fig:best-update}).
\end{algo}

@@

\noindent
Next, we convert the input \SWTA $A$ over $\Omega$
into a \SWVPA $A'$ over $\hat\Omega$, using Lemma~\ref{lem:SWTA}, 
and we compute the \SWVPA $A_{T', s} \otimes A'$, 
using Proposition~\ref{prop:SWVPA-product}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% BIBLIO                                                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{plain}
%\bibliographystyle{plainurl} 
\bibliographystyle{abbrv}
%\bibliographystyle{splncs04}
%\bibliographystyle{eptcs}
%\bibliography{generic}

>>>>

% default style article.cls
%\input{main-article}

@@

% LIPICS v.2021 style
% https://submission.dagstuhl.de/documentation/authors
\input{main-lipics}

@@

%% algorithms
%\usepackage{algorithm} 
%\usepackage{program} 
\usepackage[ruled,vlined]{algorithm2e}

@@

\noindent
Iterate the following for all $p_1\in P$ and $q_1, q_2 \in Q$:
for all $p_2\in P$ and $q_3 \in Q$,
\[
\wei'_1\bigl( \< p_1, q_1>, \< p_2, q_3>\bigr) \opluseq 
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2) 
\otimes 
\wei'_1\bigl( \< p_1, q_2>, \< p_2, q_3>\bigr)
\]
and
\(
\final'(p_1, q_1) \opluseq 
\displaystyle\bigoplus_{\Sigma} \wei_{10}(q_1, q_2) 
\otimes \final'(p_1, q_2)
\) 
\marginpar{\tiny proof correctness}
%\qed
\end{proof}

@@

\begin{algorithm}
\SetKw{Extract}{extract}
\SetKw{Update}{update}

\textbf{initially} let $\Q = (Q \times Q) \cup (Q \times P \times Q)$, %contains all 
and let $d_\bot(q_1, q_2) = d_\top(q_1, p, q_2) = \one$ if $q_1 = q_2$ and $d_\bot(q_1, q_2) = d_\top(q_1, p, q_2) = \zero$ otherwise$\;$

\smallskip\noindent
\While{$\Q \neq \emptyset$}{

%\noindent\quad
\Extract $\< q_1, q_2>$ or $\< q_1, p, q_2>$ from $\Q$
%
%\noindent\quad
such that $d_\bot(q_1, q_2)$, resp. $\bigoplus_{c\in \Omegac} d_\top(q_1, p, q_2)(c)$, is minimal in $\Semiring$ wrt $\leq_\oplus$$\;$

%\noindent\quad 
%\textbf{for all} $q_0, q_3 \in Q$ 
\Update $d_\bot$ with $\< q_1, q_2>$ or $d_\top$ with $\< q_1, p, q_2>$ (Figure~\ref{fig:best-update}).$\;$
}
\caption{Best search for \SWVPA}
\label{algo:Dijkstra}
\end{algorithm}

@@

\noindent
Next, we convert the input \SWTA $A$ over $\Omega$
into a \SWVPA $A'$ over $\hat\Omega$, using Proposition~\ref{lem:SWTA}, 
and we compute the \SWVPA $A_{T', s} \otimes A'$, 
using Proposition~\ref{prop:SWVPA-product}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% BIBLIO                                                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bibliographystyle{plain}
%\bibliographystyle{abbrv}
\bibliographystyle{plainurl}  % LIPICS
%\bibliographystyle{splncs04} % LLNCS
%\bibliographystyle{eptcs}    % EPTCS
%\bibliography{generic}
